### 2024-08-12 simulation.qmd
Built site for gh-pages

  results <- lapply(player_ids, function(player_id){
    player_data <- position_df %>% filter(id == player_id)

    # Run the simulation for this player
    simulations <- replicate(num_simulations, {
      sampled_data <- player_data %>%
        summarise(across(
          c(pass_yds, pass_tds, rush_yds, rush_tds, rec_yds, rec_tds), 
          ~ if (all(is.na(.))) NA else sample(.[!is.na(.)], 1, replace = TRUE)))

      sampled_data
    }, simplify = FALSE)

    simulation_df <- bind_rows(simulations)
    #simulation_df$fantasyPoints <- calculate_fantasyPoints(simulation_df)

>>>>

  results <- lapply(player_ids, function(player_id){ # use curly brackets when there are multiple expressions
    player_data <- position_df %>% filter(id == player_id)

    # Run the simulation for this player
    simulations <- replicate(
      num_simulations, {
        sampled_data <- player_data %>%
          summarise(across(
            c(pass_yds, pass_tds, rush_yds, rush_tds, rec_yds, rec_tds), # add more statistical categories
            ~ if (all(is.na(.))) NA else sample(.[!is.na(.)], 1, replace = TRUE)))

        sampled_data # return last expression
        }, 
      simplify = FALSE)

    simulation_df <- dplyr::bind_rows(simulations)
    #simulation_df$fantasyPoints <- calculate_fantasyPoints(simulation_df) # write function to calculate fantasy points
